Type Safe Redis Queries

### 2016-06-17 aplas16/sections/Conclusions.tex
Finished a round of revision...

None of the type-level programming techniques we used in this paper are
particularly new. Indexed monads (also called parameterized monads) have been
introduced by Atkey~\cite{indexedmonad}.
Kiselyov et al~\cite{typefun} used indexed monads to track the locks held among
a given finite set. The same paper also demonstrated implementation of a
variety of features including memoization, generic maps, session types, typed \texttt{printf} and \texttt{sprintf}, etc., by type-level programming.
Before the introduction of type families, Kiselyov and Shan~\cite{staticresources} used type classes and functional dependencies to
implement type-level functions, and showed that they are sufficient to track
resources in device drivers.

\cite{constraintskinds}

Lindley and McBride~\cite{phasedistinction} provided a good tutorial, analysis, and summary of the dependent type like features currently in Haskell, and
compared them with ``real'' dependently typed languages.

>>>>

None of the type-level programming techniques we used in this paper are
particularly new. Indexed monads (also called parameterized monads) have been
introduced by Atkey~\cite{indexedmonad}. McBride~\cite{kleisli} showed how to
construct indexed free-monads from Hoare Logic specifications.
Kiselyov et al~\cite{typefun} used indexed monads to track the locks held among
a given finite set. The same paper also demonstrated implementation of a
variety of features including memoization, generic maps, session types, typed \texttt{printf} and \texttt{sprintf}, etc., by type-level programming.
Before the introduction of type families, Kiselyov and Shan~\cite{staticresources} used type classes and functional dependencies to
implement type-level functions, and showed that they are sufficient to track
resources in device drivers.

% \cite{constraintskinds}

Lindley and McBride~\cite{phasedistinction} provided a through analysis and summary of the dependent-type-like features currently in Haskell, and
compared them with dependently typed languages without phase distinction, such as Agda. It turns out that GHC's constraint solver work surprisingly well as a theorem
prover.
